---
title: "C2016 Negative Binomial Regression Analyses"
author: "Juan Ospina"
date: "2018/9/12"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', 
  dpi = 75, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
# install.packages(c("RColorBrewer", "reshape2", "tidyverse"))
# install.packages("apaTables", dependencies = TRUE)
# install.packages("ez",dependencies = TRUE)
# install.packages("devtools")
# devtools::install_github("dstanley4/apaTables")
# library(apaTables)
library(magrittr)
# library(Hmisc)
library(RColorBrewer)
library(reshape2)
library(tidyverse)
library(emmeans) # to get adjusted means and to plot the summary statistics of models
library(kableExtra)
library(psych)
library(apaTables)
library(ez)
library(grid) # For iterative plots
library(gridExtra) # For iterative plots
# library(MASS)
# library(dplyr) # Load dplyr after MASS to be able to use select()
```

```{r data files}
d <- read_rds("../data/2019_1_22_c2016_syfus_inst_healthrec_ctra_no_t7_frosh_soph_junior.rds")
options(contrasts = c("contr.helmert", "contr.poly")) # ANOVA contrasts

# file_hr_data <- "~/Documents/Stanford Medical Records/data_for_analysis/c2016_visits_to_doctor.rds"
# d_hr <- read_rds(file_hr_data)
# 
# d %>% select(starts_with("visits_per_day")) %>% filter(!is.na(visits_per_day)) %>%
#   setdiff(d_hr %>% select(starts_with("visits_per_day")))
```

```{r custom functions}
n_obs <- function(x) sum(!is.na(x))
mn <- function(x) round(mean(x, na.rm = TRUE), 2)
mdn <- function(x) median(x, na.rm = TRUE)
std <- function(x) round(sd(x, na.rm = TRUE), 2)
lb <- function(x) round(mean(x, na.rm = TRUE) - sd(x, na.rm = TRUE), 2)
ub <- function(x) round(mean(x, na.rm = TRUE) + sd(x, na.rm = TRUE), 2)

 cv_compute <- function(data, cv_name, cv_vector){
   cv_name <- enquo(cv_name)
   data %>% 
       rowwise() %>% 
       mutate(!!quo_name(cv_name) := mean(c(!!!cv_vector), na.rm = TRUE)) %>% 
       ungroup()
 }

sum_stats_round_new2 <- function(data, factor1, factor2, variable) {
  ftr1 <- enquo(factor1)
  ftr2 <- enquo(factor2)
  var <- enquo(variable)
  
  data %>% 
    group_by(!!!ftr1, !!!ftr2) %>% 
    summarise(
      n = n_obs(!!!var),
      mean = mn(!!!var),
      median = mdn(!!!var),
      sd = std(!!!var),
      lower = lb(!!!var),
      upper = ub(!!!var))
}

geom_flat_violin <-
  function(mapping = NULL,
           data = NULL,
           stat = "ydensity",
           position = "dodge",
           trim = TRUE,
           scale = "area",
           show.legend = NA,
           inherit.aes = TRUE,
           ...) {
    ggplot2::layer(
      data = data,
      mapping = mapping,
      stat = stat,
      geom = GeomFlatViolin,
      position = position,
      show.legend = show.legend,
      inherit.aes = inherit.aes,
      params = list(trim = trim,
                    scale = scale,
                    ...)
    )
  }

GeomFlatViolin <-
  ggproto(
    "GeomFlatViolin",
    Geom,
    setup_data = function(data, params) {
      data$width <- data$width %||%
        params$width %||% (resolution(data$x, FALSE) * 0.9)
      
      # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
      data %>%
        dplyr::group_by(.data = ., group) %>%
        dplyr::mutate(
          .data = .,
          ymin = min(y),
          ymax = max(y),
          xmin = x,
          xmax = x + width / 2
        )
    },
    
    draw_group = function(data, panel_scales, coord)
    {
      # Find the points for the line to go all the way around
      data <- base::transform(data,
                              xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))
      
      # Make sure it's sorted properly to draw the outline
      newdata <-
        base::rbind(
          dplyr::arrange(.data = base::transform(data, x = xminv), y),
          dplyr::arrange(.data = base::transform(data, x = xmaxv), -y)
        )
      
      # Close the polygon: set first and last point the same
      # Needed for coord_polar and such
      newdata <- rbind(newdata, newdata[1,])
      
      ggplot2:::ggname("geom_flat_violin",
                       GeomPolygon$draw_panel(newdata, panel_scales, coord))
    },
    
    draw_key = draw_key_polygon,
    
    default_aes = ggplot2::aes(
      weight = 1,
      colour = "grey20",
      fill = "white",
      size = 0.5,
      alpha = NA,
      linetype = "solid"
    ),
    
    required_aes = c("x", "y")
  )

```

```{r custom functions correlations}
corstarsl <- function(x){ 
require(Hmisc) 
x <- as.matrix(x) 
R <- rcorr(x)$r 
p <- rcorr(x)$P 

## define notions for significance levels; spacing is important.
mystars <- ifelse(p < .001, " ***", 
                  ifelse(p < .01, " **", 
                         ifelse(p < .05, " *", # significant
                                ifelse(p < 0.1, " ??", # marginal
                                       ifelse(p < 0.15, " .", " "))))) # trending

## trunctuate the matrix that holds the correlations to two decimal
R <- format(round(cbind(rep(-1.11, ncol(x)), R), 3))[,-1] 

## build a new matrix that includes the correlations with their apropriate stars 
Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x)) 
diag(Rnew) <- paste(diag(R), " ", sep="") 
rownames(Rnew) <- colnames(x) 
colnames(Rnew) <- paste(colnames(x), "", sep="") 

## remove upper triangle
Rnew <- as.matrix(Rnew)
Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
Rnew <- as.data.frame(Rnew) 

## remove last column and return the matrix (which is now a data frame)
Rnew <- cbind(Rnew[1:length(Rnew)-1])
return(Rnew) 
}

corr_table <- function(df, vars){
  df %>% # then
  select(!!!vars) %>%
  corstarsl() %>% 
  rownames_to_column(., var = "var") %>% 
  mutate(var = new_row_names(.$var)) %>%
  # new_col_names %>% 
  slice(-1) %>% 
  kable(format = "html") %>% 
  kable_styling(bootstrap_options = c("hover", "responsive"), font_size = 12, full_width = F)
}

new_col_names <- function(df) {
  df %>% 
    rename(
      ` ` = var,
       `Happiness` = happy_comp4,
       `Life Satisfaction` = lifesat,
       `Meaning and Purpose` = purpose_comp2,
       `Daily Stress` = stressdaily,
       `Perceived Stress` = pss_comp4,
       `Time to Relax` = health_behavrelax,
       `Overall MH` = mhealthgeneral,
       `Anxiety` = anxscreener_comp2,
       `Depression` = depscreener_comp2
    )
}

new_row_names <- . %>% 
str_replace("qualitiesind_comp3", "Independence Valued") %>% # College experience
  str_replace("qualitiesinter_2_comp4", "Interdependence Valued") %>%
  str_replace("igm_comp2", "Institutional Mindsets: General") %>%
  str_replace("igmmajor1_2_3_comp3", "Institutional Mindsets: Major") %>%
  str_replace("cthreat_minorities", "Contextual Threat: Others") %>%
  str_replace("critf_distinguish_r", "Critical Feedback: To Distinguish Bwtn Students") %>%
  str_replace("critf_grow", "Critical Feedback: To Help Students Grow") %>% 
  str_replace("coll_caresuccess", "College: Success of Students") %>% 
  str_replace("wft_highstandards", "Wise Feedback Task: Prof. High standards") %>% 
  str_replace("happy_comp4", "Happiness") %>% # Well-being
  str_replace("lifesat", "Life Satisfaction") %>% 
  str_replace("purpose_comp2", "Meaning and Purpose") %>% 
  str_replace("stressdaily", "Daily Stress") %>% 
  str_replace("pss_comp4", "Perceived Stress") %>% 
  str_replace("health_behavrelax", "Time to Relax") %>% 
  str_replace("mhealthgeneral", "Overall MH") %>% 
  str_replace("anxscreener_comp2", "Anxiety") %>% 
  str_replace("depscreener_comp2", "Depression") %>%
  str_replace("visits_per_day_mh", "# of Days Visited Related to MH") %>% 
  str_replace("threat_nogen_comp8", "Threat composite  (w/out gender)") %>% #threat and health; #naming?
  str_replace("threat_comp10", "Threat composite") %>% #naming?
  str_replace("ctrarank_comp", "CTRA rank") %>% 
  str_replace("healthmosoverall_comp5", "General Physical Health (self-reported)") %>%
  str_replace("bmi", "BMI") %>%
  str_replace("visits_per_day_resp", "# of Days Visited (Respiratory Illness)") %>%
  str_replace("visits_per_day_no_resp", "# of Days Visited (No Respiratory Illness)") %>%
  str_replace("visits_per_day", "# of Days Visited") %>%
  str_replace("bingedrink_yes", "% Binge Drink") %>%
  str_replace("tobaccouse_yes", "% Tobacco Use") %>%
  str_replace("health_behavsleepiness", "Sleeping Problems")
```

```{r bar plot settings}
# These elements are not going to change from plot to plot, so I added them here so we don't have to copy paste unnecesary code
pd1 <- position_dodge()
pd2 <- position_dodge(0.1)
pd3 <- position_dodge(width = 0.9)
black1 <- element_text(color = "White")
black2 <- element_rect(fill = "black", colour = "Black", size = NULL, linetype = NULL, color = "Black", inherit.blank = FALSE)

theme1 <- theme_light()
# theme1 <- theme_classic()
guides_no <- guides(fill = FALSE)
pd4 <- position_stack(vjust = 1.1)

color_treat <- scale_fill_manual("legend", values = c("ctl" = "salmon", "treat" = "#56B4E9")) # add only to graphs between treatment and control

positions_treat <- c("ctl", "treat")

labels_treat <- scale_x_discrete(labels = c('Control','Treatment'), limits = positions_treat)

positions_cond <- c("ctl", "bel", "cul", "wf")

labels_cond <- scale_x_discrete(labels = c('Control', 'Belonging','Culture', 'Wise\nFeedback'), limits = positions_cond)

color_cond <- scale_fill_manual("legend", values = c("ctl" = "#F8766D", "bel" = "#7CAE00", "cul" = "#00BFC4", "wf" = "#C77CFF"))

adv_names <- 
  c('adv'="Advantaged",
    'disadv'="Disadvantaged")

gend_names <- 
  c('m'="Male",
    'f'="Female")

tob_names <-
  c('0' = "Non-smoking",
    '1' = "Smoking")

fgen_names <-
  c('not first-gen' = "Continuing-Generation",
    'first-gen' = "First-Generation")

race_names <-
  c('white/asian' = "Majority",
    'black/hispanic/native/pacificislander' = "Minority")

group_levels_disadv <- c('adv','disadv')
```

```{r custom functions describe sample}
table.describe <- function(data, vector){
  data %>% select(!!!vector) %>% describe %>% round(., digits = 2) %>% kable 
}
```

```{r custom functions extra}
moveme <- function(data, tomove, where = "last", ba = NULL) {
  temp <- setdiff(names(data), tomove)
  x <- switch(
    where,
    first = data[c(tomove, temp)],
    last = data[c(temp, tomove)],
    before = {
      if (is.null(ba)) stop("must specify ba column")
      if (length(ba) > 1) stop("ba must be a single character string")
      data[append(temp, values = tomove, after = (match(ba, temp)-1))]
    },
    after = {
      if (is.null(ba)) stop("must specify ba column")
      if (length(ba) > 1) stop("ba must be a single character string")
      data[append(temp, values = tomove, after = (match(ba, temp)))]
    })
  x
}

kable_format <- . %>% 
  kable(format = "html") %>% 
  kable_styling(bootstrap_options = c("hover", "responsive"), font_size = 12, full_width = F)
```

```{r}
geom_flat_violin <-
  function(mapping = NULL,
           data = NULL,
           stat = "ydensity",
           position = "dodge",
           trim = TRUE,
           scale = "area",
           show.legend = NA,
           inherit.aes = TRUE,
           ...) {
    ggplot2::layer(
      data = data,
      mapping = mapping,
      stat = stat,
      geom = GeomFlatViolin,
      position = position,
      show.legend = show.legend,
      inherit.aes = inherit.aes,
      params = list(trim = trim,
                    scale = scale,
                    ...)
    )
  }

GeomFlatViolin <-
  ggproto(
    "GeomFlatViolin",
    Geom,
    setup_data = function(data, params) {
      data$width <- data$width %||%
        params$width %||% (resolution(data$x, FALSE) * 0.9)
      
      # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
      data %>%
        dplyr::group_by(.data = ., group) %>%
        dplyr::mutate(
          .data = .,
          ymin = min(y),
          ymax = max(y),
          xmin = x,
          xmax = x + width / 2
        )
    },
    
    draw_group = function(data, panel_scales, coord)
    {
      # Find the points for the line to go all the way around
      data <- base::transform(data,
                              xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))
      
      # Make sure it's sorted properly to draw the outline
      newdata <-
        base::rbind(
          dplyr::arrange(.data = base::transform(data, x = xminv), y),
          dplyr::arrange(.data = base::transform(data, x = xmaxv), -y)
        )
      
      # Close the polygon: set first and last point the same
      # Needed for coord_polar and such
      newdata <- rbind(newdata, newdata[1,])
      
      ggplot2:::ggname("geom_flat_violin",
                       GeomPolygon$draw_panel(newdata, panel_scales, coord))
    },
    
    draw_key = draw_key_polygon,
    
    default_aes = ggplot2::aes(
      weight = 1,
      colour = "grey20",
      fill = "white",
      size = 0.5,
      alpha = NA,
      linetype = "solid"
    ),
    
    required_aes = c("x", "y")
  )

raincloud_point <- function(data, factor, mn) {
  ftr <- enquo(factor)
  mn <- enquo(mn)
  
geom_point(data = data, aes_(x = ftr, y = mn), 
             position = position_nudge(x = 0.3), size = 1.5)
}

raincloud_theme <- 
  theme(text = element_text(size = 10),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, vjust = 0),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.position = "right",
        plot.title = element_text(lineheight = .8, face = "bold", size = 16),
        panel.border = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line.x = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
        axis.line.y = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
        strip.text = element_text(color = "Black"), strip.background = element_blank())

raincloud_boxplot <-
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5)

raincloud_guides <- 
  guides(fill = FALSE, color = FALSE)
  
raincloud_theme_light <- 
  theme_light()

raincloud_violin <- 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)

stat_summary_se <- 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1, position = position_nudge(x = .3, y = 0))
```


# General Notes

All the analyses are using simple contrasts. Follow this link if you would like to know more:

https://stats.idre.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables/

All the following analyses are shown in two different versions: 

1.    Not controlling for covariates
1.    Controlling the following covariates: Gender, High School Rank, Whether the High School ranked students or not, and SAT/ACT scores

If we are controlling for other covariates, we will add notes about this before showing the graph.

# Descriptive Statistics

```{r list of variables}
source("../Cohort 2016/c2016_lists_variables_settings_plots.R")
```

## Overall
```{r}
d %>% 
  select(!!!vars_count) %>% 
  describe %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "dv_name") %>% 
  mutate_at(vars(-dv_name), funs(round(., digits = 2))) %>% 
  kable_format
```

## By Treatment and Disadvatanged Status

```{r}
treat_adv <- list(d$treat_sc, d$disadv_sc)

d %>% 
  select(!!!vars_count) %>% 
  describeBy(treat_adv, mat = TRUE, digits = 2) %>% 
  kable_format
```

## By Condition and Disadvatanged Status

```{r}
cond_adv <- list(d$cond_sc, d$disadv_sc)

d %>% 
  select(!!!vars_count) %>% 
  describeBy(cond_adv, mat = TRUE, digits = 2) %>% 
  kable_format
```

# Raincloud plots

## By Treatment and Disadvantaged Status

```{r}
theme <- 
  theme(
    strip.text = black1, 
    strip.background = black2, 
    axis.text.y = # change size of y-axis text
      element_text(
        size = 20, 
        family = "Helvetica"),
    axis.text.x = # change size of x-axis and y-axis text
      element_text(
        size = 
          20
          # 16
        , 
        family = "Helvetica"),
    axis.title = element_text(size = 22, family = "Helvetica"), 
    strip.text.x = element_text(size = 22, colour = "white", family = "Helvetica"),
    plot.title = element_text(size = 22, hjust = 0.5),
    plot.subtitle = element_text(size = 16, hjust = 0.5),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = 'top',
    legend.key = element_rect(size = 10),
    legend.key.size = unit(1, 'lines')
  )

plot_raincloud_map_treat_adv <- function(ftr, var, y_lab, scales, limit, subheader) d %>% 
  ggplot(aes(y = get(var), x = get(ftr), fill = get(ftr))) +
  raincloud_violin +
  geom_point(aes(y = get(var), color = get(ftr)), 
             position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary_se + raincloud_boxplot + raincloud_guides + 
  raincloud_theme_light + raincloud_theme +
  color_treat + labels_treat + theme1 + theme + 
  # ylab(y_lab) + xlab("") + 
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(disadv_sc), labeller = as_labeller(adv_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  # facet_grid(, vars(adv_hispanic_sc), labeller = as_labeller(hispanic_adv_names)) + 
  ylab("") + ggtitle(y_lab) + xlab("") + theme + guides_no +
  labs(subtitle = subheader)

plots <- mapply(plot_raincloud_map_treat_adv, # function
       tribble_count[,"treat_sc"] %>% t, tribble_count[,"dv"] %>% t, # arguments
       tribble_count[,"dv_name"] %>% t, tribble_count[,"scale"] %>% t, 
       tribble_count[,"limit"] %>% t, tribble_count[,"subheader"] %>% t, 
       SIMPLIFY = FALSE
       )

# plots[[41]]
# plots[[42]]
# plots[[43]]
# plots[[44]]
# plots[[45]]
plots
```

# Models

## Example
```{r}
MASS::glm.nb(visits_per_day ~ treat_sc * disadv_sc, data = d) %>% 
  summary
```

```{r}
#Transforming negative binomial coefficients to incidence rate ratios.
coef.irr <- function(model) {
  
coef_exp <- exp(coef(model))
model_se <- coef(summary(model))[, 2]
irr_se <- coef_exp*model_se
irr_confint <- exp(confint(model))

model_z <- coef(summary(model))[, 3]
model_p <- coef(summary(model))[, 4]
ratio_est <- cbind(coef_exp, irr_se, model_z, model_p, irr_confint)
colnames(ratio_est) <- c("IRR (Ratio)", "IRR.SE", "statistic", "p.value", "LL 2.5%", "UL 97.5%")

ratio_est %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  mutate_at(vars(-rowname), funs(round(., 2)))
}
```

```{r}
vars_ivs <- quos(idnum, disadv_sc, treat_sc, cond_sc,
                 sattoact, hsrank, hsrank_no, gender)

d.gather <- d %>%
  select(!!!vars_ivs, !!!vars_count) %>% 
  gather(key = dv_name, value = dv_value, !!!vars_count)

# d.gather %>% select(idnum, dv_name, dv_value)

d.nest <- 
  d.gather %>% 
  group_by(dv_name) %>% 
  nest()

# d.nest$glance[[1]]

glm_model <- function(data){
  MASS::glm.nb(dv_value ~ treat_sc * disadv_sc, data = data)
}

glm_model_cond <- function(data){
  MASS::glm.nb(dv_value ~ cond_sc * disadv_sc, data = data)
}

d.nest %<>% mutate(glm_model = map(.x = data, .f = glm_model),
                   glm_model_cond = map(.x = data, .f = glm_model_cond))

d.nest %<>%
  mutate(
    glance = glm_model %>% map(broom::glance),
    tidy = glm_model %>% map(broom::tidy),
    tidy_irr = glm_model %>% map(coef.irr),
    augment = glm_model %>% map(broom::augment),
    glance_cond = glm_model_cond %>% map(broom::glance),
    tidy_cond = glm_model_cond %>% map(broom::tidy),
    tidy_cond_irr = glm_model_cond %>% map(coef.irr),
    augment_cond = glm_model_cond %>% map(broom::augment)
  )

d.nest %<>% 
  mutate(
    emmean_treat = pmap( # Treatment effect
      .l = list(
        object = glm_model, 
        specs = "treat_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_treat_df = map(
      .x = emmean_treat, 
      .f = data.frame),
    emmean_treat_sc = map(
      .x = emmean_treat,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_treat_sc_df = map(
      .x = emmean_treat_sc, 
      .f = data.frame),
    
    emmean_treat_b = pmap( # Treatment effect (beta)
      .l = list(
        object = glm_model, 
        specs = "treat_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_treat_b_df = map(
      .x = emmean_treat_b, 
      .f = data.frame),
    emmean_treat_b_sc = map(
      .x = emmean_treat_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_treat_b_sc_df = map(
      .x = emmean_treat_b_sc, 
      .f = data.frame),
    
    emmean_ineq_treat = pmap( # Disadvantaged Inequality by Treatment
      .l = list(
        object = glm_model, 
        specs = "disadv_sc", 
        by = "treat_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_ineq_treat_df = map(
      .x = emmean_ineq_treat, 
      .f = data.frame),
    emmean_ineq_treat_sc = map(
      .x = emmean_ineq_treat,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_treat_sc_df = map(
      .x = emmean_ineq_treat_sc, 
      .f = data.frame),
    
    emmean_ineq_treat_b = pmap( # Disadvantaged Inequality by Treatment
      .l = list(
        object = glm_model, 
        specs = "disadv_sc", 
        by = "treat_sc"
      ),
      .f = emmeans
      # type = "response" 
    ),
    emmean_ineq_treat_b_df = map(
      .x = emmean_ineq_treat_b, 
      .f = data.frame),
    emmean_ineq_treat_b_sc = map(
      .x = emmean_ineq_treat_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_treat_b_sc_df = map(
      .x = emmean_ineq_treat_b_sc, 
      .f = data.frame),
    
    emmean_cond = pmap( # Condition effects
      .l = list(
        object = glm_model_cond, 
        specs = "cond_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_cond_df = map(
      .x = emmean_cond, 
      .f = data.frame),
    emmean_cond_sc = map(
      .x = emmean_cond,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_cond_sc_df = map(
      .x = emmean_cond_sc, 
      .f = data.frame),
    
    emmean_cond_b = pmap( # Condition effects (beta)
      .l = list(
        object = glm_model_cond, 
        specs = "cond_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_cond_b_df = map(
      .x = emmean_cond_b, 
      .f = data.frame),
    emmean_cond_b_sc = map(
      .x = emmean_cond_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_cond_b_sc_df = map(
      .x = emmean_cond_b_sc, 
      .f = data.frame),
    
    emmean_ineq_cond = pmap( # Disadvantaged Inequality by Condition
      .l = list(
        object = glm_model_cond, 
        specs = "disadv_sc", 
        by = "cond_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_ineq_cond_df = map(
      .x = emmean_ineq_cond, 
      .f = data.frame),
    emmean_ineq_cond_sc = map(
      .x = emmean_ineq_cond,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_cond_sc_df = map(
      .x = emmean_ineq_cond_sc, 
      .f = data.frame),
    
    emmean_ineq_cond_b = pmap( # Disadvantaged Inequality by Condition (beta)
      .l = list(
        object = glm_model_cond, 
        specs = "disadv_sc", 
        by = "cond_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_ineq_cond_b_df = map(
      .x = emmean_ineq_cond_b, 
      .f = data.frame),
    emmean_ineq_cond_b_sc = map(
      .x = emmean_ineq_cond_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_cond_b_sc_df = map(
      .x = emmean_ineq_cond_b_sc, 
      .f = data.frame)
  )
```

## Glance Overall Fit of Models

## By Treatment

```{r}
dvs_col <- 
  d.gather %>% 
  select(dv_name) %>% 
  unique

dvs_col %>% 
  bind_cols(d.nest$glance %>% bind_rows) %>% 
  kable_format
```

## By Condition

```{r}
dvs_col %>% 
  bind_cols(d.nest$glance_cond %>% bind_rows) %>% 
  kable_format
```


## Main Effects and Interactions

### By Treatment and Disadvantaged Status
#### Regular Summary of Models
```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 4) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$tidy_irr %>% bind_rows) %>% 
  kable_format
```

### By Condition and Disadvantaged Status

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 8) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy_cond %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$tidy_cond_irr %>% bind_rows) %>% 
  kable_format
```
## Simple Effects

### Disadvantaged Inequality By Any Treatment

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 2) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_treat_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_treat_sc_df %>% bind_rows) %>% 
  kable_format
```

### Treatment Effects

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 2) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_treat_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_treat_sc_df %>% bind_rows) %>% 
  kable_format
```

### Disadvantaged Inequality By Each Condition

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 4) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_cond_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_cond_sc_df %>% bind_rows) %>% 
  kable_format
```

### Condition Effects

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 12) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_cond_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_cond_sc_df %>% bind_rows) %>% 
  kable_format
```

# Bar Plots

## By Treatment and Disadvantaged Status

```{r}
d.unnest_treat <-
  d.nest %>% 
  unnest(emmean_treat_df) %>% 
  spread(key = dv_name, value = response) # change to the name of the column depending to the model

# d.nest$emmean_treat_df[[1]]
```

```{r}
theme <- 
  theme(
    strip.text = black1, 
    strip.background = black2, 
    axis.text = element_text(size = 20, family = "Helvetica"),
    axis.title = element_text(size = 20, family = "Helvetica"), 
    strip.text.x = element_text(size = 20, colour = "white", family = "Helvetica"),
    plot.title = element_text(size = 24, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = 'top',
    legend.key = element_rect(size = 10),
    legend.key.size = unit(1, 'lines')
  )

guides_no <- guides(fill = FALSE, color = FALSE)

legend_treat <- scale_color_manual(name = "", 
                                  values = c("ctl" = "salmon", 
                                             "treat" = "steelblue2"))

plot_bar_x_y_group_treat_adv <- function(ftr, var, y_lab, scales, limit,
                                         position,
                                         # decimal, 
                                         subheader
                                         ) d.unnest_treat %>% 
  filter(!is.na(get(var))) %>% 
  ggplot(aes(x = get(ftr), y = get(var), color = get(ftr), group = get(ftr))) + # Remember to add get()
  # geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), size = 42, color = "black") +
  geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), size = 41) +
  geom_errorbar(aes(ymin = get(var) - SE, ymax = get(var) + SE), width = .4, position = pd2, color = "black") +
  theme1 +
  # geom_text(aes(label = format(get(var)*100, digits = 4), y = 10), size = 8, color = "black") +
  geom_text(aes(label = format(paste0(round(get(var), digits = 2)), digits = 3), y = position), 
            size = 8, color = "black") +
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(disadv_sc), labeller = as_labeller(adv_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  ylab("") + ggtitle(y_lab) + xlab("") + theme + guides_no +
  labs(subtitle = subheader) +
  labels_treat + color_treat + legend_treat

plots <- mapply(plot_bar_x_y_group_treat_adv, # function
       tribble_count[,"treat_sc"] %>% t,  # arguments
       tribble_count[,"dv"] %>% t,
       tribble_count[,"dv_name"] %>% t, 
       tribble_count[,"scale"] %>% t, 
       tribble_count[,"limit"] %>% t, 
       tribble_count[,"position"] %>% t,
       # tribble_count[,"decimal"] %>% t, 
       tribble_count[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```

## By Condition and Disadvantaged Status

```{r}
d.unnest_cond <-
  d.nest %>% 
  unnest(emmean_cond_df) %>% 
  spread(key = dv_name, value = response)
```

```{r}
theme_cond <- 
  theme(
    strip.text = black1, 
    strip.background = black2, 
    axis.text = element_text(size = 12, family = "Helvetica"),  # change size of conditions labels 
    axis.title = element_text(size = 18, family = "Helvetica"), 
    strip.text.x = element_text(size = 14, colour = "white", family = "Helvetica"), # change size of factor labels 
    plot.title = element_text(size = 24, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = 'top',
    legend.key = element_rect(size = 10),
    legend.key.size = unit(1, 'lines')
  )

guides_no <- guides(fill = FALSE, color = FALSE)

legend_cond <- scale_color_manual(name = "", 
                                  values = c("ctl" = "#F8766D", 
                                             "bel" = "#7CAE00", 
                                             "cul" = "#00BFC4", 
                                             "wf" = "#C77CFF"))

plot_bar_x_y_group_cond_adv <- function(ftr, var, y_lab, scales, limit,
                                         position,
                                         # decimal, 
                                         subheader
                                         ) d.unnest_cond %>% 
  filter(!is.na(get(var))) %>% 
  ggplot(aes(x = get(ftr), y = get(var), color = get(ftr), group = get(ftr))) + # Remember to add get()
  # geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), size = 42, color = "black") +
  geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), size = 23) +
  geom_errorbar(aes(ymin = get(var) - SE, ymax = get(var) + SE), width = .4, position = pd2, color = "black") +
  theme1 +
  # geom_text(aes(label = format(get(var)*100, digits = 4), y = 10), size = 8, color = "black") +
  geom_text(aes(label = format(paste0(round(get(var), digits = 2)), digits = 3), y = position), 
            size = 5, color = "black") +
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(disadv_sc), labeller = as_labeller(adv_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  ylab("") + ggtitle(y_lab) + xlab("") + theme_cond + guides_no +
  labs(subtitle = subheader) +
  labels_cond + color_cond + legend_cond

plots <- mapply(plot_bar_x_y_group_cond_adv, # function
       tribble_count[,"cond_sc"] %>% t,  # arguments
       tribble_count[,"dv"] %>% t,
       tribble_count[,"dv_name"] %>% t, 
       tribble_count[,"scale"] %>% t, 
       tribble_count[,"limit"] %>% t, 
       tribble_count[,"position"] %>% t,
       # tribble_count[,"decimal"] %>% t, 
       tribble_count[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```

# Models with covariates

## Example
```{r}
MASS::glm.nb(visits_per_day ~ treat_sc * disadv_sc + gender + sattoact + hsrank + hsrank_no, data = d) %>% 
  summary
```

```{r}
glm_model_treat_cv <- function(data){
  MASS::glm.nb(dv_value ~ treat_sc * disadv_sc + gender + sattoact + hsrank + hsrank_no, data = data)
}

glm_model_cond_cv <- function(data){
  MASS::glm.nb(dv_value ~ cond_sc * disadv_sc + gender + sattoact + hsrank + hsrank_no, data = data)
}

d.nest %<>% mutate(glm_model_treat_cv = map(.x = data, .f = glm_model_treat_cv),
                   glm_model_cond_cv = map(.x = data, .f = glm_model_cond_cv))

d.nest %<>%
  mutate(
    glance_treat_cv = glm_model_treat_cv %>% map(broom::glance),
    tidy_treat_cv = glm_model_treat_cv %>% map(broom::tidy),
    tidy_treat_cv_irr = glm_model_treat_cv %>% map(coef.irr),
    augment_cv = glm_model_treat_cv %>% map(broom::augment),
    glance_cond_cv = glm_model_cond_cv %>% map(broom::glance),
    tidy_cond_cv = glm_model_cond_cv %>% map(broom::tidy),
    tidy_cond_cv_irr = glm_model_cond_cv %>% map(coef.irr),
    augment_cond_cv = glm_model_cond_cv %>% map(broom::augment)
  )

d.nest %<>% 
  mutate(
    emmean_treat_cv = pmap( # Treatment effects
      .l = list(
        object = glm_model_treat_cv, 
        specs = "treat_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_treat_cv_df = map(
      .x = emmean_treat_cv, 
      .f = data.frame),
    emmean_treat_cv_sc = map(
      .x = emmean_treat_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_treat_cv_sc_df = map(
      .x = emmean_treat_cv_sc, 
      .f = data.frame),
    
    emmean_treat_cv_b = pmap( # Treatment effects (beta)
      .l = list(
        object = glm_model_treat_cv, 
        specs = "treat_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_treat_cv_b_df = map(
      .x = emmean_treat_cv_b, 
      .f = data.frame),
    emmean_treat_cv_b_sc = map(
      .x = emmean_treat_cv_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_treat_cv_b_sc_df = map(
      .x = emmean_treat_cv_b_sc, 
      .f = data.frame),
    
    emmean_ineq_treat_cv = pmap( # Disadvantaged Inequality by treatment
      .l = list(
        object = glm_model_treat_cv, 
        specs = "disadv_sc", 
        by = "treat_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_ineq_treat_cv_df = map(
      .x = emmean_ineq_treat_cv, 
      .f = data.frame),
    emmean_ineq_treat_cv_sc = map(
      .x = emmean_ineq_treat_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_treat_cv_sc_df = map(
      .x = emmean_ineq_treat_cv_sc, 
      .f = data.frame),
    
    emmean_ineq_treat_cv_b = pmap( # Disadvantaged Inequality by treatment (beta)
      .l = list(
        object = glm_model_treat_cv, 
        specs = "disadv_sc", 
        by = "treat_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_ineq_treat_cv_b_df = map(
      .x = emmean_ineq_treat_cv_b, 
      .f = data.frame),
    emmean_ineq_treat_cv_b_sc = map(
      .x = emmean_ineq_treat_cv_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_treat_cv_b_sc_df = map(
      .x = emmean_ineq_treat_cv_b_sc, 
      .f = data.frame),
    
    emmean_cond_cv = pmap( # condition effects
      .l = list(
        object = glm_model_cond_cv, 
        specs = "cond_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_cond_cv_df = map(
      .x = emmean_cond_cv, 
      .f = data.frame),
    emmean_cond_cv_sc = map(
      .x = emmean_cond_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_cond_cv_sc_df = map(
      .x = emmean_cond_cv_sc, 
      .f = data.frame),
    
    emmean_cond_cv_b = pmap( # condition effects (beta)
      .l = list(
        object = glm_model_cond_cv, 
        specs = "cond_sc", 
        by = "disadv_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_cond_cv_b_df = map(
      .x = emmean_cond_cv_b, 
      .f = data.frame),
    emmean_cond_cv_b_sc = map(
      .x = emmean_cond_cv_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_cond_cv_b_sc_df = map(
      .x = emmean_cond_cv_b_sc, 
      .f = data.frame),
    
    emmean_ineq_cond_cv = pmap( # Disadvantaged Inequality by condition
      .l = list(
        object = glm_model_cond_cv, 
        specs = "disadv_sc", 
        by = "cond_sc"
      ),
      .f = emmeans,
      type = "response"
    ),
    emmean_ineq_cond_cv_df = map(
      .x = emmean_ineq_cond_cv, 
      .f = data.frame),
    emmean_ineq_cond_cv_sc = map(
      .x = emmean_ineq_cond_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_cond_cv_sc_df = map(
      .x = emmean_ineq_cond_cv_sc, 
      .f = data.frame),
    
    emmean_ineq_cond_cv_b = pmap( # Disadvantaged Inequality by condition (beta)
      .l = list(
        object = glm_model_cond_cv, 
        specs = "disadv_sc", 
        by = "cond_sc"
      ),
      .f = emmeans
      # type = "response"
    ),
    emmean_ineq_cond_cv_b_df = map(
      .x = emmean_ineq_cond_cv_b, 
      .f = data.frame),
    emmean_ineq_cond_cv_b_sc = map(
      .x = emmean_ineq_cond_cv_b,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_cond_cv_b_sc_df = map(
      .x = emmean_ineq_cond_cv_b_sc, 
      .f = data.frame)
  ) 
```

## Glance Overall Fit of Models

## By Treatment

```{r}
dvs_col <- 
  d.gather %>% 
  select(dv_name) %>% 
  unique

dvs_col %>% 
  bind_cols(d.nest$glance_treat_cv %>% bind_rows) %>% 
  kable_format
```

## By Condition

```{r}
dvs_col %>% 
  bind_cols(d.nest$glance_cond_cv %>% bind_rows) %>% 
  kable_format
```

## Main Effects and Interactions

### By Treatment and Disadvantaged Status
#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 8) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy_treat_cv %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$tidy_treat_cv_irr %>% bind_rows) %>% 
  kable_format
```


### By Condition and Disadvantaged Status

#### Regular Summary of Models
```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 12) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy_cond_cv %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$tidy_cond_cv_irr %>% bind_rows) %>% 
  kable_format
```

## Simple Effects

### Disadvantaged Inequality By Any Treatment

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 2) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_treat_cv_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_treat_cv_sc_df %>% bind_rows) %>% 
  kable_format
```

### Treatment Effects

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 2) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_treat_cv_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_treat_cv_sc_df %>% bind_rows) %>% 
  kable_format
```

### Disadvantaged Inequality By Each Condition

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 4) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_cond_cv_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_cond_cv_sc_df %>% bind_rows) %>% 
  kable_format
```

### Condition Effects

#### Regular Summary of Models

```{r}
dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 12) %>% # change this number depending on the number of rows of your tidy datasets
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_cond_cv_b_sc_df %>% bind_rows) %>% 
  kable_format
```

#### Incidence Rate Ratio Summary of Models

```{r}
dvs_col_rep %>% 
  bind_cols(d.nest$emmean_cond_cv_sc_df %>% bind_rows) %>% 
  kable_format
```

# Bar Plots with covariates

## By Treatment and Disadvantaged Status

```{r}
d.unnest_treat <-
  d.nest %>% 
  unnest(emmean_treat_cv_df) %>% 
  spread(key = dv_name, value = response)
```

```{r}
plots <- mapply(plot_bar_x_y_group_treat_adv, # function
       tribble_count[,"treat_sc"] %>% t,  # arguments
       tribble_count[,"dv"] %>% t,
       tribble_count[,"dv_name"] %>% t, 
       tribble_count[,"scale"] %>% t, 
       tribble_count[,"limit"] %>% t, 
       tribble_count[,"position"] %>% t,
       # tribble_count[,"decimal"] %>% t, 
       tribble_count[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```

## By Condition and Disadvantaged Status

```{r}
d.unnest_cond <-
  d.nest %>% 
  unnest(emmean_cond_cv_df) %>% 
  spread(key = dv_name, value = response)
```

```{r}
plots <- mapply(plot_bar_x_y_group_cond_adv, # function
       tribble_count[,"cond_sc"] %>% t,  # arguments
       tribble_count[,"dv"] %>% t,
       tribble_count[,"dv_name"] %>% t, 
       tribble_count[,"scale"] %>% t, 
       tribble_count[,"limit"] %>% t, 
       tribble_count[,"position"] %>% t,
       # tribble_count[,"decimal"] %>% t, 
       tribble_count[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```
