---
title: "C2016 Linear Regression Analyses: First-Generation Status and Race"
author: "Juan Ospina"
date: "2018/9/12"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', 
  dpi = 75, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
# install.packages(c("RColorBrewer", "reshape2", "tidyverse"))
# install.packages("apaTables", dependencies = TRUE)
# install.packages("ez",dependencies = TRUE)
# , "kableExtra", "psych", "ez", "grid", "gridExtra"
# devtools::install_github("dstanley4/apaTables")
library(magrittr)
library(RColorBrewer)
library(reshape2)
library(tidyverse)
library(emmeans) # to get adjusted means and to plot the summary statistics of models
library(kableExtra)
library(psych)
library(apaTables)
library(ez)
library(grid) # For iterative plots
library(gridExtra) # For iterative plots
# library(MASS)
# library(dplyr) # Load dplyr after MASS to be able to use select()
```

```{r data files}
# For Juan
d <- read_rds("../data/2018_4_2_c2016_syfus_inst_healthrec_ctra_no_t7.rds")

# For RAs
# d <- read_rds("../../../Box Sync/Research Assistants/data/2018_4_2_c2016_syfus_inst_healthrec_ctra_no_t7.rds")

options(contrasts = c("contr.helmert", "contr.poly")) # ANOVA contrasts
```

```{r custom functions}
n_obs <- function(x) sum(!is.na(x))
mn <- function(x) round(mean(x, na.rm = TRUE), 2)
mdn <- function(x) median(x, na.rm = TRUE)
std <- function(x) round(sd(x, na.rm = TRUE), 2)
lb <- function(x) round(mean(x, na.rm = TRUE) - sd(x, na.rm = TRUE), 2)
ub <- function(x) round(mean(x, na.rm = TRUE) + sd(x, na.rm = TRUE), 2)

 cv_compute <- function(data, cv_name, cv_vector){
   cv_name <- enquo(cv_name)
   data %>% 
       rowwise() %>% 
       mutate(!!quo_name(cv_name) := mean(c(!!!cv_vector), na.rm = TRUE)) %>% 
       ungroup()
 }

sum_stats_round_new2 <- function(data, factor1, factor2, variable) {
  ftr1 <- enquo(factor1)
  ftr2 <- enquo(factor2)
  var <- enquo(variable)
  
  data %>% 
    group_by(!!!ftr1, !!!ftr2) %>% 
    summarise(
      n = n_obs(!!!var),
      mean = mn(!!!var),
      median = mdn(!!!var),
      sd = std(!!!var),
      lower = lb(!!!var),
      upper = ub(!!!var))
}

geom_flat_violin <-
  function(mapping = NULL,
           data = NULL,
           stat = "ydensity",
           position = "dodge",
           trim = TRUE,
           scale = "area",
           show.legend = NA,
           inherit.aes = TRUE,
           ...) {
    ggplot2::layer(
      data = data,
      mapping = mapping,
      stat = stat,
      geom = GeomFlatViolin,
      position = position,
      show.legend = show.legend,
      inherit.aes = inherit.aes,
      params = list(trim = trim,
                    scale = scale,
                    ...)
    )
  }

GeomFlatViolin <-
  ggproto(
    "GeomFlatViolin",
    Geom,
    setup_data = function(data, params) {
      data$width <- data$width %||%
        params$width %||% (resolution(data$x, FALSE) * 0.9)
      
      # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
      data %>%
        dplyr::group_by(.data = ., group) %>%
        dplyr::mutate(
          .data = .,
          ymin = min(y),
          ymax = max(y),
          xmin = x,
          xmax = x + width / 2
        )
    },
    
    draw_group = function(data, panel_scales, coord)
    {
      # Find the points for the line to go all the way around
      data <- base::transform(data,
                              xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))
      
      # Make sure it's sorted properly to draw the outline
      newdata <-
        base::rbind(
          dplyr::arrange(.data = base::transform(data, x = xminv), y),
          dplyr::arrange(.data = base::transform(data, x = xmaxv), -y)
        )
      
      # Close the polygon: set first and last point the same
      # Needed for coord_polar and such
      newdata <- rbind(newdata, newdata[1,])
      
      ggplot2:::ggname("geom_flat_violin",
                       GeomPolygon$draw_panel(newdata, panel_scales, coord))
    },
    
    draw_key = draw_key_polygon,
    
    default_aes = ggplot2::aes(
      weight = 1,
      colour = "grey20",
      fill = "white",
      size = 0.5,
      alpha = NA,
      linetype = "solid"
    ),
    
    required_aes = c("x", "y")
  )

```

```{r raincloud plots custom functions}
plot_raincloud <- function(data, factor, variable, x_color, labs_y, labels_x, 
                           scale, coord_cartesian, group_var, group_names, theme) {
  ftr <- enquo(factor)
  var <- enquo(variable)
  group_var <- enquo(group_var)
  
  data %>% 
    ggplot(aes_(y = var, x = ftr, fill = ftr)) +
    raincloud_violin +
    geom_point(aes_(y = var, color = ftr), 
               position = position_jitter(width = .15), size = .5, alpha = 0.8) +
    stat_summary_se + raincloud_boxplot + raincloud_guides + raincloud_theme_light + raincloud_theme +
    x_color + labs_y + labels_x + theme1 + theme +
    scale + coord_cartesian +
    facet_grid(, vars(!!group_var), labeller = as_labeller(group_names)) # ignore warning, this is to make the plot facet the variables in the way that we want it
}

# Example:
# d %>% 
# ggplot(aes(y = healthmosoverall_comp5, x = treat, fill = treat)) +
#   raincloud_violin +
#   geom_point(aes(y = healthmosoverall_comp5, color = treat), 
#              position = position_jitter(width = .15), size = .5, alpha = 0.8) +
#   geom_point(data = sum_stats_healthmosoverall_comp5_treat, aes(x = treat, y = mean),
#              position = position_nudge(x = 0.3), size = 1.5) +
#   stat_summary_se + raincloud_boxplot + raincloud_guides + raincloud_theme_light + raincloud_theme +
#   facet_grid(~ disadv) +
#   labs(x = "Condition", y = "Overall physical health", fill = "Condition")


raincloud_point <- function(data, factor, mn) {
  ftr <- enquo(factor)
  mn <- enquo(mn)
  
geom_point(data = data, aes_(x = ftr, y = mn), 
             position = position_nudge(x = 0.3), size = 1.5)
}

raincloud_theme <- 
  theme(text = element_text(size = 10),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, vjust = 0),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.position = "right",
        plot.title = element_text(lineheight = .8, face = "bold", size = 16),
        panel.border = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line.x = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
        axis.line.y = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
        strip.text = element_text(color = "Black"), strip.background = element_blank())

raincloud_boxplot <-
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5)

raincloud_guides <- 
  guides(fill = FALSE, color = FALSE)
  
raincloud_theme_light <- 
  theme_light()

raincloud_violin <- 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)

stat_summary_se <- 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1, position = position_nudge(x = .3, y = 0))
```

```{r bar plot settings}
# These elements are not going to change from plot to plot, so I added them here so we don't have to copy paste unnecesary code
pd1 <- position_dodge()
pd2 <- position_dodge(0.1)
pd3 <- position_dodge(width = 0.9)
black1 <- element_text(color = "White")
black2 <- element_rect(fill = "black", colour = "Black", size = NULL, linetype = NULL, color = "Black", inherit.blank = FALSE)

# theme <- theme(strip.text = black1, strip.background = black2, axis.text = element_text(size = 14),
#         axis.title = element_text(size = 14), strip.text.x = element_text(size = 14, colour = "white"),
#         panel.grid.major = element_blank(), panel.grid.minor = element_blank())

theme.cond <- theme(strip.text = black1, strip.background = black2, axis.text = element_text(size = 12),
        axis.title = element_text(size = 14), strip.text.x = element_text(size = 14, colour = "white"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

theme1 <- theme_light()
# theme1 <- theme_classic()
guides_no <- guides(fill = FALSE)
pd4 <- position_stack(vjust = 1.1)

color_treat <- scale_fill_manual(name = "", 
                                 values = c("ctl" = "salmon", 
                                            "treat" = "#56B4E9")) # add only to graphs between treatment and control

legend_treat <- scale_color_manual(name = "", 
                                  values = c("ctl" = "salmon", 
                                             "treat" = "steelblue2"))

positions_treat <- c("ctl", "treat")

# labels_treat <- scale_x_discrete(labels = c('Control','Treatment'), limits = positions_treat)
labels_treat <- 
  scale_x_discrete(labels = c('X','T'), limits = positions_treat)

positions_cond <- c("ctl", "bel", "cul", "wf")

# labels_cond <- scale_x_discrete(labels = c('Control', 'Belonging','Culture', 'Wise\nFeedback'), limits = positions_cond)
labels_cond <- 
  scale_x_discrete(
    labels = c('X', 'B','C', 'F'), 
    limits = positions_cond
    )

color_cond <- scale_fill_manual("legend", 
                                values = c("ctl" = "#F8766D", 
                                           "bel" = "#7CAE00", 
                                           "cul" = "#00BFC4", 
                                           "wf" = "#C77CFF"))

legend_cond <- scale_color_manual(name = "", 
                                  values = c("ctl" = "#F8766D", 
                                             "bel" = "#7CAE00", 
                                             "cul" = "#00BFC4", 
                                             "wf" = "#C77CFF"))

adv_names <- 
  c('adv'="Advantaged",
    'disadv'="Disadvantaged")

gend_names <- 
  c('m'="Male",
    'f'="Female")

# tob_names <-
#   c('0' = "Non-smoking",
#     '1' = "Smoking")

fgen_names <-
  c('not first-gen' = "Continuing-Generation",
    'first-gen' = "First-Generation")

race_names <-
  c('white/asian' = "Majority",
    'black/hispanic/native/pacificislander' = "Minority")

group_levels_disadv <- c('adv','disadv')

firstgen_race_names <- 
  c('adv' = "Advantaged",
    'black' = "Black",
    'hispanic' = "Hispanic",
    'pi.native' = "Pacific/Native",
    'white first-gen' = "White FG")

firstgen_race_names <- 
  c('white CG' = "White CG",
    'white FG' = "White FG",
    'asian CG' = "Asian CG",
    'asian FG' = "Asian FG",
    'minority CG' = "Minority CG",
    'minority FG' = "Minority FG")

```

```{r custom functions describe sample}
table.describe <- function(data, vector){
  data %>% select(!!!vector) %>% describe %>% round(., digits = 2) %>% kable 
}
```

```{r load custom functions}
source("R/custom_functions.R")
```

# General Notes

```{r}
d %>% 
  count(firstgen_race_sc, firstgen_race_num) %>% 
  kable_format
```

All the analyses are using simple contrasts. Follow this link if you would like to know more:

https://stats.idre.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables/

All the following analyses are shown in two different versions: 

1.    Not controlling for covariates
1.    Controlling the following covariates: Gender, High School Rank, Whether the High School ranked students or not, and SAT/ACT scores

If we are controlling for other covariates, we will add notes about this before showing the graph.

# Descriptive Statistics

```{r list of variables}
source("c2016_lists_variables_settings_plots.R")
```

## Overall

```{r}
vars_cont <- 
  quos(
    overallmentalhealth_comp5_z,
    bmi_chge_scr,
    threat_nogen_comp8,
    integ_idrace,
    activism_engaged
  ) 
```

```{r}
# rownames_to_column(as.data.frame(describe(select(d, !!!vars_cont))), var = "dv_name")

d %>% 
  select(!!!vars_cont) %>% 
  describe %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "dv_name") %>% 
  mutate_at(vars(-dv_name), funs(round(., digits = 2))) %>% 
  kable_format
```

## By Treatment and Advantaged Status and Minority

```{r}
treat_adv <- list(d$treat_sc, 
                  d$firstgen_race_sc
                  # d$adv_hispanic_sc
                  )

d %>% 
  select(!!!vars_cont) %>% 
  describeBy(treat_adv, mat = TRUE, digits = 2) %>% 
  kable_format
```

## By Condition and Advantaged Status and Minority

```{r}
cond_adv <- list(d$cond_sc, 
                 d$firstgen_race_sc
                 # d$adv_hispanic_sc
                 )

d %>% 
  select(!!!vars_cont) %>% 
  describeBy(cond_adv, mat = TRUE, digits = 2) %>% 
  kable_format
```

# Raincloud plots

## By Treatment and Advantaged and Minority Students

```{r}
tribble_cont %<>% 
  filter(
    dv == "overallmentalhealth_comp5_z" |
      dv == "bmi_chge_scr" |
      dv == "threat_nogen_comp8" |
      dv == "integ_idrace" |
      dv == "activism_engaged"
  )
```

```{r}
theme <- 
  theme(
    strip.text = black1, 
    strip.background = black2, 
    axis.text.y = # change size of y-axis text
      element_text(
        size = 20, 
        family = "Helvetica"),
    axis.text.x = # change size of x-axis text
      element_text(
        size = 
          # 20
          14
        , 
        family = "Helvetica"),
    axis.title = element_text(size = 22, family = "Helvetica"), 
    strip.text.x = element_text(size = 12, colour = "white", family = "Helvetica"),
    plot.title = element_text(size = 22, hjust = 0.5),
    plot.subtitle = element_text(size = 16, hjust = 0.5),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = 'top',
    legend.key = element_rect(size = 10),
    legend.key.size = unit(1, 'lines')
  )

plot_raincloud_map_treat_adv <- function(ftr, var, y_lab, scales, limit, subheader) d %>% 
  ggplot(aes(y = get(var), x = get(ftr), fill = get(ftr))) +
  raincloud_violin +
  geom_point(aes(y = get(var), color = get(ftr)), 
             position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary_se + raincloud_boxplot + raincloud_guides + 
  raincloud_theme_light + raincloud_theme +
  color_treat + labels_treat + theme1 + theme + 
  # ylab(y_lab) + xlab("") + 
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(firstgen_race_sc), labeller = as_labeller(firstgen_race_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  # facet_grid(, vars(adv_hispanic_sc), labeller = as_labeller(hispanic_adv_names)) + 
  ylab("") + ggtitle(y_lab) + xlab("") + theme + guides_no +
  labs(subtitle = subheader)

plots <- mapply(plot_raincloud_map_treat_adv, # function
       tribble_cont[,"treat_sc"] %>% t, tribble_cont[,"dv"] %>% t, # arguments
       tribble_cont[,"dv_name"] %>% t, tribble_cont[,"scale"] %>% t, 
       tribble_cont[,"limit"] %>% t, tribble_cont[,"subheader"] %>% t, 
       SIMPLIFY = FALSE
       )

plots
```

## By Condition and Advantaged and Minority Students

```{r}
theme_cond <- 
  theme(
    strip.text = black1, 
    strip.background = black2, 
    axis.text.y = # change size of y-axis text
      element_text(
        size = 20, 
        family = "Helvetica"),
    axis.text.x = # change size of x-axis text
      element_text(
        size = 
          12
        , 
        family = "Helvetica"),
    axis.title = element_text(size = 18, family = "Helvetica"), 
    strip.text.x = 
      element_text(size = 12, colour = "white", family = "Helvetica"), # change size of factor labels 
    plot.title = element_text(size = 18, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    # axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = 'top',
    legend.key = element_rect(size = 10),
    legend.key.size = unit(1, 'lines')
  )


plot_raincloud_map_cond_adv <- function(ftr, var, y_lab, scales, limit, subheader) d %>% 
  ggplot(aes(y = get(var), x = get(ftr), fill = get(ftr))) +
  raincloud_violin +
  geom_point(aes(y = get(var), color = get(ftr)), 
             position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  stat_summary_se + raincloud_boxplot + raincloud_guides + 
  raincloud_theme_light + raincloud_theme +
  color_cond + labels_cond + theme1 + theme_cond + 
  # ylab(y_lab) + xlab("") + 
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(firstgen_race_sc), labeller = as_labeller(firstgen_race_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  # facet_grid(, vars(adv_hispanic_sc), labeller = as_labeller(hispanic_adv_names)) + 
  ylab("") + ggtitle(y_lab) + xlab("") + theme_cond + guides_no +
  labs(subtitle = subheader)

plots <- mapply(plot_raincloud_map_cond_adv, # function
       tribble_cont[,"cond_sc"] %>% t, tribble_cont[,"dv"] %>% t, # arguments
       tribble_cont[,"dv_name"] %>% t, tribble_cont[,"scale"] %>% t, 
       tribble_cont[,"limit"] %>% t, tribble_cont[,"subheader"] %>% t, 
       SIMPLIFY = FALSE
       )

plots
```

# Effect sizes

## Is there inequality?

We want to focus on the effect sizes between advantaged and advantaged and minority students  in the control group.

### Inequalities between advantaged and advantaged and minority students  in control

Effect sizes (Cohen's *d*) between advantaged and advantaged and minority students  in control:

```{r}
cohend_ineq <- 
  cohen.d.by(x = d %>% 
               select(treat_num, 
                      firstgen_race_num,
                      # adv_hispanic_num,
                      !!!vars_cont), 
             group = "firstgen_race_num",
             # group = "adv_hispanic_num",
             group2 = "treat_num", 
             alpha = .05) 

cohend_ineq

# cohend_ineq <- 
#   cohend_ineq %>%
#   rownames_to_column() %>% 
#   filter(rowname == "firstgen_race_numfortreat_num0") %>%
#   select(-rowname) %>%
#   round(., digits = 2)
```

## Is there a Advantaged and Minority Students effect?

### Differences between advantaged and disadvantaged for all conditions

```{r}
cohend_disadv_all <- 
  cohen.d(d %>% 
            select(
              firstgen_race_num,
              # adv_hispanic_num,
              !!!vars_cont), 
          group = 
            "firstgen_race_num",
            # "adv_hispanic_num",
          alpha = .05)

cohend_disadv_all

# cohend_disadv_all <- cohend_disadv_all$cohen.d
# 
# cohend_disadv_all %<>% as.data.frame() %>% rownames_to_column()
# 
# cohend_disadv_all
```

## Is there a treatment effect?

### Differences between control and any treatment for all students

```{r}
cohend_treat_all <- 
  cohen.d(
    d %>% 
      select(treat_num, 
             !!!vars_cont), 
    group = "treat_num", 
    alpha = .05
    )

# cohend_treat_all <- cohend_treat_all$cohen.d
# 
# cohend_treat_all %<>% as.data.frame() %>% rownames_to_column()

cohend_treat_all
```

### Differences between control and belonging for all students

```{r}
cohend_bel_all <- cohen.d(d %>% select(cd_bel_num, !!!vars_cont), group = "cd_bel_num", alpha = .05)

cohend_bel_all
```

### Differences between control and culture for all students

```{r}
cohend_cul_all <- cohen.d(d %>% select(cd_cul_num, !!!vars_cont), group = "cd_cul_num", alpha = .05)

cohend_cul_all
```

### Differences between control and wise feedback for all students

```{r}
cohend_wf_all <- cohen.d(d %>% select(cd_wf_num, !!!vars_cont), group = "cd_wf_num", alpha = .05)

cohend_wf_all
```

### Differences between control and any treatment for advantaged and minority students 

Effect sizes (Cohen's *d*) between control and any treatment for advantaged and advantaged and minority students :

```{r eval=FALSE, include=FALSE}
# d %>% count(disadv, firstgen_race_num) %>% select(-n)

cohend_treat <- 
  cohen.d.by(
    x = d %>% 
      select(
        treat_num, 
        firstgen_race_num,
        # adv_hispanic_num,
        !!!vars_cont), 
    group = "treat_num", 
    group2 = 
      "firstgen_race_num",
      # "adv_hispanic_num",
    alpha = .05)

# %>% summary

# cohend_treat %<>% 
#   rownames_to_column() %>% 
#   # filter(rowname == "treat_numforfirstgen_race_num1") %>% 
#   select(-rowname) %>%
#   round(., digits = 2)

cohend_treat
```

### Differences between control and each condition for advantaged and advantaged and minority students 

#### Belonging

```{r eval=FALSE, include=FALSE}
cohend_bel <- 
  cohen.d.by(
    x = d %>% 
      select(
        cd_bel_num,
        firstgen_race_num,
        # adv_hispanic_num,
        !!!vars_cont
        ), 
    group = "cd_bel_num", 
    group2 = 
      "firstgen_race_num",
      # "adv_hispanic_num",
    alpha = .05
    )

# %>% summary

# cohend_bel %<>% 
#   rownames_to_column() %>% 
#   # filter(rowname == "cd_bel_numforfirstgen_race_num1") %>% 
#   select(-rowname) %>% 
#   round(., digits = 2)

cohend_bel
```

#### Culture
```{r eval=FALSE, include=FALSE}
cohend_cul <- 
  cohen.d.by(
    x = d %>% 
      select(
        cd_cul_num, 
        firstgen_race_num,
        # adv_hispanic_num,
        !!!vars_cont
        ), 
    group = "cd_cul_num", 
    group2 = 
      "firstgen_race_num",
      # "adv_hispanic_num",
    alpha = .05
    ) 

# %>% summary

# cohend_cul %<>% 
#   rownames_to_column() %>% 
#   # filter(rowname == "cd_cul_numforfirstgen_race_num1") %>% 
#   select(-rowname) %>% 
#   round(., digits = 2)

cohend_cul
```

#### Wise Feedback
```{r eval=FALSE, include=FALSE}
cohend_wf <- 
  cohen.d.by(
    x = d %>% 
      select(
        cd_wf_num, 
        firstgen_race_num,
        # adv_hispanic_sc,
        !!!vars_cont
        ), 
    group = "cd_wf_num", 
    group2 = 
      "firstgen_race_num",
      # "adv_hispanic_sc",
    alpha = .05) 

# %>% summary

# cohend_wf %<>% 
#   rownames_to_column() %>% 
#   # filter(rowname == "cd_wf_numforfirstgen_race_num1") %>% 
#   select(-rowname) %>% 
#   round(., digits = 2)

cohend_wf
```

# Models

## Example
```{r}
lm(cum_gpa_y4_spring ~ 
     treat_sc*firstgen_race_sc,
   # treat_sc*adv_hispanic_sc,
   data = d
   ) %>% summary
```

```{r}
# d.model <- d %>% select(treat_sc, firstgen_race_sc, !!!vars_cont)
# 
# models_lm <- d.model %>% select(-c(treat_sc, firstgen_race_sc)) %>%
#   map(function(dv) lm(dv ~ d$treat_sc*d$firstgen_race_sc, data = .)) 
```

```{r}
vars_ivs <- 
  quos(
    idnum, # IDs
    firstgen_race_sc, # groups
    treat_sc, cond_sc, # conditions
    sattoact, hsrank, hsrank_no, gender # covariates
  )

d.gather <- d %>%
  select(!!!vars_ivs, !!!vars_cont) %>% 
  gather(key = dv_name, value = dv_value, !!!vars_cont)

# d.gather %>% select(idnum, dv_name, dv_value)

d.nest <- 
  d.gather %>% 
  group_by(dv_name) %>% 
  nest()

# d.nest$data[[1]]

lm_model <- function(data){
  lm(dv_value ~ treat_sc*firstgen_race_sc, data = data)
  # lm(dv_value ~ treat_sc*adv_hispanic_sc, data = data)
}

lm_model_cond <- function(data){
  lm(dv_value ~ cond_sc*firstgen_race_sc, data = data)
  # lm(dv_value ~ cond_sc*adv_hispanic_sc, data = data)
}

d.nest %<>% mutate(lm_model = map(.x = data, .f = lm_model),
                   lm_model_cond = map(.x = data, .f = lm_model_cond))

d.nest %<>%
  mutate(
    glance = lm_model %>% map(broom::glance),
    rsq = glance %>% map_dbl("r.squared"),
    tidy = lm_model %>% map(broom::tidy),
    augment = lm_model %>% map(broom::augment),
    glance_cond = lm_model_cond %>% map(broom::glance),
    rsq_cond = glance_cond %>% map_dbl("r.squared"),
    tidy_cond = lm_model_cond %>% map(broom::tidy),
    augment_cond = lm_model_cond %>% map(broom::augment)
  )

d.nest %<>% 
  mutate(
    emmean_treat = pmap( # treatment effects by Advantaged and Minority Students
      .l = list(
        object = lm_model, 
        specs = "treat_sc", 
        by = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
      ),
      .f = emmeans
    ),
    emmean_treat_df = map(
      .x = emmean_treat, 
      .f = data.frame),
    emmean_treat_sc = map(
      .x = emmean_treat,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_treat_sc_df = map(
      .x = emmean_treat_sc, 
      .f = data.frame),
    
    emmean_ineq_treat = pmap( # Inequality of Advantaged and Minority Students by treatment
      .l = list(
        object = lm_model, 
        specs = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
        , 
        by = "treat_sc"
      ),
      .f = emmeans
    ),
    emmean_ineq_treat_df = map(
      .x = emmean_ineq_treat, 
      .f = data.frame),
    emmean_ineq_treat_sc = map(
      .x = emmean_ineq_treat,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_treat_sc_df = map(
      .x = emmean_ineq_treat_sc, 
      .f = data.frame),
    
    emmean_cond = pmap( # Condition effects by Advantaged and Minority Students
      .l = list(
        object = lm_model_cond, 
        specs = "cond_sc", 
        by = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
      ),
      .f = emmeans
    ),
    emmean_cond_df = map(
      .x = emmean_cond, 
      .f = data.frame),
    emmean_cond_sc = map(
      .x = emmean_cond,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_cond_sc_df = map(
      .x = emmean_cond_sc, 
      .f = data.frame),
    
    emmean_ineq_cond = pmap( # Inequality of Advantaged and Minority Students by any condition
      .l = list(
        object = lm_model_cond, 
        specs = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
        , 
        by = "cond_sc"
      ),
      .f = emmeans
    ),
    emmean_ineq_cond_df = map(
      .x = emmean_ineq_cond, 
      .f = data.frame),
    emmean_ineq_cond_sc = map(
      .x = emmean_ineq_cond,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_cond_sc_df = map(
      .x = emmean_ineq_cond_sc, 
      .f = data.frame)
  ) 
```

## Glance Overall Fit of Models

## By Treatment

```{r}
dvs_col <- 
  d.gather %>% 
  select(dv_name) %>% 
  unique

dvs_col %>% 
  bind_cols(d.nest$glance %>% bind_rows) %>% 
  round_table(quos(dv_name), 2) %>% 
  kable_format
```

## By Condition

```{r}
dvs_col %>% 
  bind_cols(d.nest$glance_cond %>% bind_rows) %>% 
  round_table(quos(dv_name), 2) %>% 
  kable_format
```


## Main Effects and Interactions

### By Treatment and Advantaged and Minority Students
```{r}
# d.nest$tidy[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        12 # change this number depending on the number of rows of your tidy datasets
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

# The variable "donate_srgifttot" is the one that has less rows. Right now it is row 99.
# check error from variable below
# bind_cols(d.nest$tidy)
# d.nest$tidy[[99]]

dvs_col_rep %>% 
  bind_cols(d.nest$tidy %>% bind_rows) %>% 
  round_table(quos(dv_name, term), 2) %>% 
  kable_format
```

### By Condition and Advantaged and Minority Students
```{r}
# d.nest$tidy_cond[[1]]

repetitions <- 
  bind_rows(d.nest$tidy_cond) %>% 
  rownames_to_column %>% 
  filter(term == "(Intercept)") %>% 
  bind_cols(dvs_col) %>% 
  select(rowname, dv_name) %>% 
  mutate(
    rowname_num = as.numeric(rowname),
    repetitions = lead(rowname_num) - rowname_num
    ) %>% 
  select(-rowname) %>% 
  rownames_to_column %>% 
  mutate(
    repetitions = ifelse(dv_name == "activism_engaged", 24, repetitions) # remember to change the last variable and the times
  )

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(
    times = 
      repetitions$repetitions # change this number depending on the number of rows of your tidy datasets
      # 12
    ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

# dvs_col_rep <- dvs_col$dv_name %>% 
#   rep(
#     times = 
#       24 # change this number depending on the number of rows of your tidy datasets
#       # 12
#     ) %>% 
#   as.tibble %>% 
#   rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy_cond %>% bind_rows) %>% 
  round_table(quos(dv_name, term), 2) %>% 
  kable_format
```

## Simple Effects

### Inequality of Advantaged and Minority Students by Treatment

```{r}
# d.nest$emmean_ineq_treat_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>%
  rep(
    each = 
      30 # change this number depending on the number of rows of your tidy datasets
      # 6
    ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_treat_sc_df %>% bind_rows) %>% 
  round_table(quos(dv_name, contrast, treat_sc), 2) %>% 
  kable_format
```

### Treatment Effects by Advantaged and Minority Students

```{r}
d.nest$emmean_treat_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(
    each = 
      6 # change this number depending on the number of rows of your tidy datasets
    ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_treat_sc_df %>% bind_rows) %>% 
  round_table(
    quos(
      dv_name, 
      contrast, 
      firstgen_race_sc
      # adv_hispanic_sc
    ), 2) %>% 
  kable_format
```

### Inequality effects of Advantaged and Minority Students
```{r}
# d.nest$emmean_ineq_cond_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>%
  rep(each = 
        60 # change this number depending on the number of rows of your tidy datasets
        # 12
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_cond_sc_df %>% bind_rows) %>% 
  round_table(quos(dv_name, contrast, cond_sc), 2) %>% 
  kable_format
```

### Condition Effects by Advantaged and Minority Students

```{r}
# d.nest$emmean_cond_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        36 # change this number depending on the number of rows of your tidy datasets
        # 18
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_cond_sc_df %>% bind_rows) %>% 
  round_table(
    quos(
      dv_name, 
      contrast, 
      firstgen_race_sc
      # adv_hispanic_sc
      ), 
    2) %>% 
  kable_format
```

# Bar Plots

## By Treatment and Advantaged and Minority Students

```{r}
d.unnest_treat <-
  d.nest %>% 
  unnest(emmean_treat_df) %>% 
  spread(key = dv_name, value = emmean)
```

```{r}
guides_no <- guides(fill = FALSE, color = FALSE)

plot_bar_x_y_group_treat_adv <- function(ftr, var, y_lab, scales, limit, position, decimal, subheader) d.unnest_treat %>% 
  filter(!is.na(get(var))) %>% 
  ggplot(aes(x = get(ftr), y = get(var), color = get(ftr), group = get(ftr))) + # Remember to add get()
  # geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), size = 42, color = "black") +
  geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), 
               size = 
                 # 41
                 14
               ) +
  geom_errorbar(aes(ymin = get(var) - SE, ymax = get(var) + SE), width = .4, position = pd2, color = "black") +
  theme1 +
  geom_text(aes(label = round(
    get(var),
    digits = 2), 
    y = position), size = 5, color = "black") +
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(firstgen_race_sc), labeller = as_labeller(firstgen_race_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  # facet_grid(, vars(adv_hispanic_sc), labeller = as_labeller(hispanic_adv_names)) +
  ylab("") + ggtitle(y_lab) + xlab("") + theme + guides_no +
  labs(subtitle = subheader) + 
  labels_treat + color_treat + legend_treat

plots <- mapply(plot_bar_x_y_group_treat_adv, # function
       tribble_cont[,"treat_sc"] %>% t, tribble_cont[,"dv"] %>% t, # arguments
       tribble_cont[,"dv_name"] %>% t, tribble_cont[,"scale"] %>% t, 
       tribble_cont[,"limit"] %>% t, tribble_cont[,"position"] %>% t, 
       tribble_cont[,"decimal"] %>% t, tribble_cont[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```

## By Condition and Advantaged and Minority Students

```{r}
d.unnest_cond <-
  d.nest %>% 
  unnest(emmean_cond_df) %>% 
  spread(key = dv_name, value = emmean)
```

```{r}
plot_bar_x_y_group_cond_adv <- function(ftr, var, y_lab, scales, limit, position, decimal, subheader) d.unnest_cond %>% 
  filter(!is.na(get(var))) %>% 
  ggplot(aes(x = get(ftr), y = get(var), color = get(ftr), group = get(ftr))) + # Remember to add get()
  # geom_segment(aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), size = 42, color = "black") +
  geom_segment(
    aes(x = get(ftr), xend = get(ftr), y = -10, yend = get(var)), 
    size = 
      # 24 # change from disadvantaged to other groups
      7.5
    ) +
  geom_errorbar(aes(ymin = get(var) - SE, ymax = get(var) + SE), width = .4, position = pd2, color = "black") +
  theme1 +
  geom_text(aes(label = round(
    get(var),
    digits = 2), 
    y = position), size = 2.8, color = "black") +
  coord_cartesian(ylim = limit) +
  scale_y_continuous(breaks = scales) +
  facet_grid(, vars(firstgen_race_sc), labeller = as_labeller(firstgen_race_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  # facet_grid(, vars(adv_hispanic_sc), labeller = as_labeller(hispanic_adv_names)) +
  ylab("") + ggtitle(y_lab) + xlab("") + theme_cond + guides_no +
  labs(subtitle = subheader) + 
  labels_cond + color_cond + legend_cond

plots <- mapply(plot_bar_x_y_group_cond_adv, # function
       tribble_cont[,"cond_sc"] %>% t, tribble_cont[,"dv"] %>% t, # arguments
       tribble_cont[,"dv_name"] %>% t, tribble_cont[,"scale"] %>% t, 
       tribble_cont[,"limit"] %>% t, tribble_cont[,"position"] %>% t, 
       tribble_cont[,"decimal"] %>% t, tribble_cont[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```

# Models with covariates

## Example
```{r}
lm(cum_gpa_y4_spring ~ 
     treat_sc*firstgen_race_sc +
     # treat_sc*adv_hispanic_sc +
     gender + sattoact + hsrank + hsrank_no, data = d) %>% summary
```

```{r}
lm_model_treat_cv <- function(data){
  lm(dv_value ~ treat_sc*firstgen_race_sc + gender + sattoact + hsrank + hsrank_no, data = data)
  # lm(dv_value ~ treat_sc*adv_hispanic_sc + gender + sattoact + hsrank + hsrank_no, data = data)
}

lm_model_cond_cv <- function(data){
  lm(dv_value ~ cond_sc*firstgen_race_sc + gender + sattoact + hsrank + hsrank_no, data = data)
  # lm(dv_value ~ cond_sc*adv_hispanic_sc + gender + sattoact + hsrank + hsrank_no, data = data)
}

d.nest %<>% mutate(lm_model_treat_cv = map(.x = data, .f = lm_model_treat_cv),
                   lm_model_cond_cv = map(.x = data, .f = lm_model_cond_cv))

d.nest %<>%
  mutate(
    glance_treat_cv = lm_model_treat_cv %>% map(broom::glance),
    rsq_treat_cv = glance_treat_cv %>% map_dbl("r.squared"),
    tidy_treat_cv = lm_model_treat_cv %>% map(broom::tidy),
    augment_cv = lm_model_treat_cv %>% map(broom::augment),
    glance_cond_cv = lm_model_cond_cv %>% map(broom::glance),
    rsq_cond_cv = glance_cond_cv %>% map_dbl("r.squared"),
    tidy_cond_cv = lm_model_cond_cv %>% map(broom::tidy),
    augment_cond_cv = lm_model_cond_cv %>% map(broom::augment)
  )

d.nest %<>% 
  mutate(
    emmean_treat_cv = pmap( # Treatment effects by Advantaged and Minority Students
      .l = list(
        object = lm_model_treat_cv, 
        specs = "treat_sc", 
        by = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
      ),
      .f = emmeans
    ),
    emmean_treat_cv_df = map(
      .x = emmean_treat_cv, 
      .f = data.frame),
    emmean_treat_cv_sc = map(
      .x = emmean_treat_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_treat_cv_sc_df = map(
      .x = emmean_treat_cv_sc, 
      .f = data.frame),
    
    emmean_ineq_treat_cv = pmap( # Inequality of Advantaged and Minority Students by treatment
      .l = list(
        object = lm_model_treat_cv, 
        specs = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
        , 
        by = "treat_sc"
      ),
      .f = emmeans
    ),
    emmean_ineq_treat_cv_df = map(
      .x = emmean_ineq_treat_cv, 
      .f = data.frame),
    emmean_ineq_treat_cv_sc = map(
      .x = emmean_ineq_treat_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_treat_cv_sc_df = map(
      .x = emmean_ineq_treat_cv_sc, 
      .f = data.frame),
    
    emmean_cond_cv = pmap( # Condition effects by Advantaged and Minority Students
      .l = list(
        object = lm_model_cond_cv, 
        specs = "cond_sc", 
        by = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
      ),
      .f = emmeans
    ),
    emmean_cond_cv_df = map(
      .x = emmean_cond_cv, 
      .f = data.frame),
    emmean_cond_cv_sc = map(
      .x = emmean_cond_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_cond_cv_sc_df = map(
      .x = emmean_cond_cv_sc, 
      .f = data.frame),
    
    emmean_ineq_cond_cv = pmap( # Inequality of Advantaged and Minority Students by condition
      .l = list(
        object = lm_model_cond_cv, 
        specs = 
          "firstgen_race_sc"
          # "adv_hispanic_sc"
        , 
        by = "cond_sc"
      ),
      .f = emmeans
    ),
    emmean_ineq_cond_cv_df = map(
      .x = emmean_ineq_cond_cv, 
      .f = data.frame),
    emmean_ineq_cond_cv_sc = map(
      .x = emmean_ineq_cond_cv,
      .f = pairs,
      reverse = TRUE,
      adjust = "none"
    ),
    emmean_ineq_cond_cv_sc_df = map(
      .x = emmean_ineq_cond_cv_sc, 
      .f = data.frame)
  ) 
```

## Glance Overall Fit of Models

## By Treatment

```{r}
# d.nest$glance_treat_cv[[1]]

dvs_col <- 
  d.gather %>% 
  select(dv_name) %>% 
  unique

dvs_col %>% 
  bind_cols(d.nest$glance_treat_cv %>% bind_rows) %>% 
  round_table(quos(dv_name), 2) %>% 
  kable_format
```

## By Condition

```{r}
# d.nest$glance_cond_cv[[1]]

dvs_col %>% 
  bind_cols(d.nest$glance_cond_cv %>% bind_rows) %>% 
  round_table(quos(dv_name), 2) %>% 
  kable_format
```

## Main Effects and Interactions

### By Treatment and Advantaged and Minority Students
```{r}
# d.nest$tidy_treat_cv[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        16 # change this number depending on the number of rows of your tidy datasets
        # 10
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy_treat_cv %>% bind_rows) %>% 
  round_table(quos(dv_name, term), 2) %>% 
  kable_format
```

### By Condition and Advantaged and Minority Students
```{r}
# d.nest$tidy_cond_cv[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        28 # change this number depending on the number of rows of your tidy datasets
        # 16
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

repetitions <- 
  bind_rows(d.nest$tidy_cond_cv) %>% # change the column of the nested dataset
  rownames_to_column %>% 
  filter(term == "(Intercept)") %>% 
  bind_cols(dvs_col) %>% 
  select(rowname, dv_name) %>% 
  mutate(
    rowname_num = as.numeric(rowname),
    repetitions = lead(rowname_num) - rowname_num
    ) %>% 
  select(-rowname) %>% 
  rownames_to_column %>% 
  mutate(
    repetitions = ifelse(dv_name == "activism_engaged", 28, repetitions) # remember to change the last variable and the times
  )

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(
    times = 
      repetitions$repetitions # change this number depending on the number of rows of your tidy datasets
      # 12
    ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$tidy_cond_cv %>% bind_rows) %>% 
  round_table(quos(dv_name, term), 2) %>% 
  kable_format
```

## Simple Effects

### Inequality of Advantaged and Minority Students by Treatment

```{r}
# d.nest$emmean_ineq_treat_cv_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        30  # change this number depending on the number of rows of your tidy datasets
        # 6
      ) %>%
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_treat_cv_sc_df %>% bind_rows) %>% 
  round_table(quos(dv_name, contrast, treat_sc), 2) %>% 
  kable_format
```

### Treatment Effects

```{r}
# d.nest$emmean_treat_cv_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        6 # change this number depending on the number of rows of your tidy datasets
        # 3
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_treat_cv_sc_df %>% bind_rows) %>% 
  round_table(
    quos(
      dv_name, 
      contrast, 
      firstgen_race_sc
      # adv_hispanic_sc
      ), 
    2) %>% 
  kable_format
```

### Inequality of Advantaged and Minority Students by Treatment

```{r}
# d.nest$emmean_ineq_cond_cv_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        60 # change this number depending on the number of rows of your tidy datasets
        # 12
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_ineq_cond_cv_sc_df %>% bind_rows) %>% 
  round_table(
    quos(
      dv_name, 
      contrast, 
      cond_sc
      ),
    2) %>% 
  kable_format
```

### Condition Effects

```{r}
# d.nest$emmean_cond_cv_sc_df[[1]]

dvs_col_rep <- dvs_col$dv_name %>% 
  rep(each = 
        36 # change this number depending on the number of rows of your tidy datasets
        # 18
      ) %>% 
  as.tibble %>% 
  rename(dv_name = value)

dvs_col_rep %>% 
  bind_cols(d.nest$emmean_cond_cv_sc_df %>% bind_rows) %>% 
  round_table(
    quos(
      dv_name, 
      contrast, 
      firstgen_race_sc
      # adv_hispanic_sc
      ),
    2) %>% 
  kable_format
```

# Bar Plots with covariates

## By Treatment and Advantaged and Minority Students

```{r}
d.unnest_treat <-
  d.nest %>% 
  unnest(emmean_treat_cv_df) %>% 
  spread(key = dv_name, value = emmean)
```

```{r}
plots <- mapply(plot_bar_x_y_group_treat_adv, # function
       tribble_cont[,"treat_sc"] %>% t, tribble_cont[,"dv"] %>% t, # arguments
       tribble_cont[,"dv_name"] %>% t, tribble_cont[,"scale"] %>% t, 
       tribble_cont[,"limit"] %>% t, tribble_cont[,"position"] %>% t, 
       tribble_cont[,"decimal"] %>% t, tribble_cont[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```

## By Condition and Advantaged and Minority Students

```{r}
d.unnest_cond <-
  d.nest %>% 
  unnest(emmean_cond_cv_df) %>% 
  spread(key = dv_name, value = emmean)
```

```{r}
plots <- mapply(plot_bar_x_y_group_cond_adv, # function
       tribble_cont[,"cond_sc"] %>% t, tribble_cont[,"dv"] %>% t, # arguments
       tribble_cont[,"dv_name"] %>% t, tribble_cont[,"scale"] %>% t, 
       tribble_cont[,"limit"] %>% t, tribble_cont[,"position"] %>% t, 
       tribble_cont[,"decimal"] %>% t, tribble_cont[,"subheader"] %>% t,
       SIMPLIFY = F)

plots
```
