---
title: "New Analyses"
author: "Juan Ospina"
date: "12/13/2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', 
  dpi = 75, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
library(magrittr)
library(RColorBrewer)
library(reshape2)
library(tidyverse)
library(emmeans) # to get adjusted means and to plot the summary statistics of models
library(kableExtra)
library(psych)
library(apaTables)
library(ez)
library(grid) # For iterative plots
library(gridExtra) # For iterative plots
library(ggplot2)
library(ggstatsplot)
```

```{r data files}
# For Juan
d <- read_rds("../data/2018_4_2_c2016_syfus_inst_healthrec_ctra_no_t7.rds")

# For RAs
# d <- read_rds("../../../Box Sync/Research Assistants/data/2018_4_2_c2016_syfus_inst_healthrec_ctra_no_t7.rds")

options(contrasts = c("contr.helmert", "contr.poly")) # ANOVA contrasts
```

```{r bar plot settings}
# These elements are not going to change from plot to plot, so I added them here so we don't have to copy paste unnecesary code
pd1 <- position_dodge()
pd2 <- position_dodge(0.1)
pd3 <- position_dodge(width = 0.9)
black1 <- element_text(color = "White")
black2 <- element_rect(fill = "black", colour = "Black", size = NULL, linetype = NULL, color = "Black", inherit.blank = FALSE)

# theme <- theme(strip.text = black1, strip.background = black2, axis.text = element_text(size = 14),
#         axis.title = element_text(size = 14), strip.text.x = element_text(size = 14, colour = "white"),
#         panel.grid.major = element_blank(), panel.grid.minor = element_blank())

theme.cond <- theme(strip.text = black1, strip.background = black2, axis.text = element_text(size = 12),
        axis.title = element_text(size = 14), strip.text.x = element_text(size = 14, colour = "white"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

theme1 <- theme_light()
# theme1 <- theme_classic()
guides_no <- guides(fill = FALSE)
pd4 <- position_stack(vjust = 1.1)

color_treat <- scale_fill_manual(name = "", 
                                 values = c("ctl" = "salmon", 
                                            "treat" = "#56B4E9")) # add only to graphs between treatment and control

legend_treat <- scale_color_manual(name = "", 
                                  values = c("ctl" = "salmon", 
                                             "treat" = "steelblue2"))

positions_treat <- c("ctl", "treat")

# labels_treat <- scale_x_discrete(labels = c('Control','Treatment'), limits = positions_treat)
labels_treat <- 
  scale_x_discrete(labels = c('X','T'), limits = positions_treat)

positions_cond <- c("ctl", "bel", "cul", "wf")

# labels_cond <- scale_x_discrete(labels = c('Control', 'Belonging','Culture', 'Wise\nFeedback'), limits = positions_cond)
labels_cond <- 
  scale_x_discrete(
    labels = c('X', 'B','C', 'F'), 
    limits = positions_cond
    )

color_cond <- scale_fill_manual("legend", 
                                values = c("ctl" = "#F8766D", 
                                           "bel" = "#7CAE00", 
                                           "cul" = "#00BFC4", 
                                           "wf" = "#C77CFF"))

legend_cond <- scale_color_manual(name = "", 
                                  values = c("ctl" = "#F8766D", 
                                             "bel" = "#7CAE00", 
                                             "cul" = "#00BFC4", 
                                             "wf" = "#C77CFF"))

adv_names <- 
  c('adv'="Advantaged",
    'disadv'="Disadvantaged")

gend_names <- 
  c('m'="Male",
    'f'="Female")

# tob_names <-
#   c('0' = "Non-smoking",
#     '1' = "Smoking")

fgen_names <-
  c('not first-gen' = "Continuing-Generation",
    'first-gen' = "First-Generation")

race_names <-
  c('white/asian' = "Majority",
    'black/hispanic/native/pacificislander' = "Minority")

group_levels_disadv <- c('adv','disadv')

minority_adv_names <- 
  c('adv' = "Advantaged",
    'black' = "Black",
    'hispanic' = "Hispanic",
    'pi.native' = "Pacific/Native",
    'white first-gen' = "White FG")
```


```{r load custom functions}
source("custom_functions/custom_functions.R")
```

# General Notes

All the analyses are using simple contrasts. Follow this link if you would like to know more:

https://stats.idre.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables/

All the following analyses are shown in two different versions: 

1.    Not controlling for covariates
1.    Controlling the following covariates: Gender, High School Rank, Whether the High School ranked students or not, and SAT/ACT scores

If we are controlling for other covariates, we will add notes about this before showing the graph.

# New Plots

```{r list of variables}
source("c2016_lists_variables_settings_plots.R")
```

```{r}
# plot
# ggstatsplot::ggbetweenstats(
#   data = d, 
#   x = treat_sc, 
#   y = purpose_comp2,
#   messages = FALSE
# ) +                                               # further modification outside of ggstatsplot
#   ggplot2::coord_cartesian(ylim = c(1, 5)) + 
#   ggplot2::scale_y_continuous(breaks = seq(1, 5, by = 1)) 


# plot
ggstatsplot::grouped_ggbetweenstats(
  data = d, 
  x = treat_sc, 
  y = purpose_comp2,
  grouping.var = disadv_sc,             # grouping variable
  pairwise.comparisons = TRUE,      # display significant pairwise comparisons
  pairwise.annotation = "p.value",  # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni",   # method for adjusting p-values for multiple comparisons
  bf.message = TRUE,                # display Bayes Factor in favor of the null hypothesis
  conf.level = 0.95,                # changing confidence level to 99%
  k = 2,                            # number of digits after decimal point
  effsize.type = "d",
  # notch = TRUE,
  # outlier.tagging = TRUE,
  caption = substitute(paste(italic("Source"), 
                             ": Senior Year Survey")),
  palette = "default_jama",
  package = "ggsci",
  messages = FALSE,
  nrow = 1,
  ncol = 2,
  title.text = "Eudaimonic Well-Being",
  xlab = "",
  ylab = ""
)

ggstatsplot::ggcoefstats(
  x = stats::lm(
    formula = purpose_comp2 ~ treat_sc * disadv_sc + sattoact + hsrank + gender + hsrank_no,
    data = d
    )
  )
```

```{r fig.width = 10, fig.asp = .8}
# plot
ggstatsplot::grouped_ggbetweenstats(
  data = d, 
  x = cond_sc, 
  y = purpose_comp2,
  grouping.var = disadv_sc,             # grouping variable
  pairwise.comparisons = TRUE,      # display significant pairwise comparisons
  pairwise.annotation = "p.value",  # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni",   # method for adjusting p-values for multiple comparisons
  bf.message = TRUE,                # display Bayes Factor in favor of the null hypothesis
  conf.level = 0.95,                # changing confidence level to 99%
  k = 2,                            # number of digits after decimal point
  effsize.type = "d",
  # notch = TRUE,
  # outlier.tagging = TRUE,
  caption = substitute(paste(italic("Source"), 
                             ": Senior Year Survey")),
  palette = "default_jama",
  package = "ggsci",
  messages = FALSE,
  nrow = 1,
  ncol = 2,
  title.text = "Eudaimonic Well-Being",
  xlab = "",
  ylab = ""
)

ggstatsplot::ggcoefstats(
  x = stats::lm(
    formula = purpose_comp2 ~ cond_sc * disadv_sc + sattoact + hsrank + gender + hsrank_no,
    data = d
    )
  )
```


