---
title: "DBSS Attrition Analyses"
author: "Juan Ospina"
date: "6/18/2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', dpi = 300, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE
) 
```

```{r}
library(magrittr)
# library(Hmisc)
library(reshape2)
library(tidyverse)
library(broman)
library(kableExtra)
# library(nnet) # multinomial logistic regression
library(car) # to generate correct output from models
library(psych)
```

```{r}
file_master_data <- "../data/2018_4_2_c2016_syfus_inst_healthrec_ctra_no_t7.rds"

d_all <- read_rds(file_master_data)
```

```{r load custom functions}
source("R/custom_functions.R")
```

```{r}
d.att <- d_all %>% filter(recruitedSYFUS == 1)
```

```{r}
variables <- quos(gender, disadvantaged, firstgen, race_amaj, race.w, race.a, race.b, race.h, race.n.pi, tobaccouse_yes, bingedrink_yes, bmi, age_4y)
```

# Attrition Analyses (All Ss who gave viable DBSS)

**Note:** These analyses include all 198 Ss who gave viable DBSS.

## Summary Statistics

```{r}
d.att %>% 
  count(usefulDBSS)

# I found these participants age after sending the file to Steve. Thus, we need to omit them when reporting the analyses
d.att %<>% 
  mutate(age_4y = 
           ifelse(idnum == "20121309" | 
                    idnum == "20121420", NA, age_4y))
```

### Overall 

```{r}
# d.att %>% filter(usefulDBSS == 1) %>% select(!!!variables) %>% describe %>% round(., digits = 2) %>% kable
```

```{r}
# d.att %>% filter(usefulDBSS == 0) %>%  select(!!!variables) %>% describe %>% round(., digits = 2) %>% kable
```

```{r}
198/212 * 100

vars_demog <-
  quos(
    gender_num,
    disadv_num,
    firstgen_num,
    race_amaj_num,
    race.w_num,
    race.a_num,
    race.b_num,
    race.h_num,
    race.n.pi_num,
    tobaccouse_yes,
    bingedrink_yes,
    bmi,
    age_4y
  )

d.att.dbss <- 
  d.att %>% 
  filter(usefulDBSS == 1) 

d.att.dbss %>% 
  select(!!!vars_demog) %>% 
  describe %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "dv_name") %>% 
  mutate_at(vars(-dv_name), funs(round(., digits = 3))) %>% 
  kable_format
```

### By Condition

```{r}
d.att.dbss %>% 
  select(!!!vars_demog) %>% 
  describeBy(d.att.dbss$cond_sc, mat = TRUE, digits = 3) %>% 
  kable_format
```

## Analyses

**Findings:** All results are non-significant except for High school rank (hsrank) and whether the high school ranked students or not (hsrank_no). 

Thus, we did not find significant differences in gender, disadvantaged status, first-generation status, race (minorities vs majorities, each race (White, Asian, Black, Latino or Hispanic, and Native/Pacific Islander), tobacco use, binge drinking, BMI, age after four years of the intervention, and SAT/ACT scores between the students that we tried to recruit for the Senior Year Follow-Up Survey (SYFUS; *N* = 375) and those who gave us analyzable DBSS (*N* = 198).

We found a *significant* difference in High School Rank such that students who gave analyzable DBSS tend to have lower High School Rank (better) compared to those that we tried to recruit for SYFUS. Also, we found a *significant* difference in whether the high school ranked students or not such that there were less students in high schools that did not rank their students who gave us analyzable DBSS compared to students in high schools that did not rank their students who we tried to recruit for SYFUS.

### Significant Tests

```{r}
lm(hsrank ~ usefulDBSS, data = d.att) %>% summary
glm(hsrank_no ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
```

### Non-significant Tests

```{r}
glm(gender ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(disadvantaged ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(firstgen ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary

glm(race_amaj ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.w ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.a ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.b ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.h ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.n.pi ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary

glm(tobaccouse_yes ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(bingedrink_yes ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
lm(bmi ~ usefulDBSS, data = d.att) %>% summary
lm(age_4y ~ usefulDBSS, data = d.att) %>% summary
lm(sattoact ~ usefulDBSS, data = d.att) %>% summary
```

## Attrition Analyses by Condition

```{r}
d.c <- d.att %>% filter(usefulDBSS == 1)
```

```{r}
chisq.test(d.c$gender, d.c$cond)
chisq.test(d.c$disadvantaged, d.c$cond)
chisq.test(d.c$firstgen, d.c$cond)

chisq.test(d.c$race_amaj, d.c$cond)
chisq.test(d.c$race.w, d.c$cond)
chisq.test(d.c$race.a, d.c$cond)
chisq.test(d.c$race.b, d.c$cond)
chisq.test(d.c$race.h, d.c$cond)
chisq.test(d.c$race.n.pi, d.c$cond)

chisq.test(d.c$tobaccouse_yes, d.c$cond)
chisq.test(d.c$bingedrink_yes, d.c$cond)

options(contrasts = c("contr.helmert", "contr.poly"))

Anova(lm(bmi ~ cond, data = d.c))
lm(bmi ~ cond, data = d.c) %>% summary
Anova(lm(age_4y ~ cond, data = d.c))
lm(age_4y ~ cond, data = d.c) %>% summary
Anova(lm(sattoact ~ cond, data = d.c))
lm(sattoact ~ cond, data = d.c) %>% summary
```

# Attrition Analyses (without participants who are missing covariates)

**Note:** These analyses include the 182 Ss who gave viable DBSS and who are not missing covariates data.

```{r}
# to remove from the sample the participants who gave DBSS but are missing covariates, run the following code
# If you want to review the analyses with all the participants, just comment this chunk code
d.att.dbss <-
  d.att %>% 
  filter(
    usefulDBSS == 1 & 
      !is.na(age_4y) & 
      !is.na(tobaccouse_yes) & 
      !is.na(bmi) &
      !is.na(bingedrink_yes) &
      !is.na(race_amaj_num) &
      !is.na(gender_num) &
      idnum != "20121309" & 
      idnum != "20121420"
    )

d.att.syfus <-
  d.att %>% 
  filter(usefulDBSS == 0)

d.att <-
  bind_rows(d.att.dbss, d.att.syfus)
```

## Summary Statistics

### Overall 

```{r}
182/212 * 100

d.att.dbss <- 
  d.att %>% 
    filter(usefulDBSS == 1)
  
d.att.dbss %>% 
  select(!!!vars_demog) %>% 
  describe %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "dv_name") %>% 
  mutate_at(vars(-dv_name), funs(round(., digits = 3))) %>% 
  kable_format
```

### By Condition

```{r}
d.att.dbss %>% 
  select(!!!vars_demog) %>% 
  describeBy(d.att.dbss$cond_sc, mat = TRUE, digits = 3) %>% 
  kable_format
```

## Analyses

**Findings:** All results are non-significant except for High school rank (hsrank) and whether the high school ranked students or not (hsrank_no). 

Thus, we did not find significant differences in gender, disadvantaged status, first-generation status, race (minorities vs majorities, each race (White, Asian, Black, Latino or Hispanic, and Native/Pacific Islander), tobacco use, binge drinking, BMI, age after four years of the intervention, and SAT/ACT scores between the students that we tried to recruit for the Senior Year Follow-Up Survey (SYFUS; *N* = 375) and those who gave us analyzable DBSS (*N* = 198).

We found a *significant* difference in High School Rank such that students who gave analyzable DBSS tend to have lower High School Rank (better) compared to those that we tried to recruit for SYFUS. Also, we found a *significant* difference in whether the high school ranked students or not such that there were less students in high schools that did not rank their students who gave us analyzable DBSS compared to students in high schools that did not rank their students who we tried to recruit for SYFUS.

### Significant Tests

```{r}
lm(hsrank ~ usefulDBSS, data = d.att) %>% summary
glm(hsrank_no ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
```

### Non-significant Tests

```{r}
glm(gender ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(disadvantaged ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(firstgen ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary

glm(race_amaj ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.w ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.a ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.b ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.h ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(race.n.pi ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary

glm(tobaccouse_yes ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
glm(bingedrink_yes ~ usefulDBSS, data = d.att, family = binomial, na.action = na.omit) %>% summary
lm(bmi ~ usefulDBSS, data = d.att) %>% summary
lm(age_4y ~ usefulDBSS, data = d.att) %>% summary
lm(sattoact ~ usefulDBSS, data = d.att) %>% summary
```

## Attrition Analyses by Condition

```{r}
d.c <- d.att %>% filter(usefulDBSS == 1)
```

```{r}
chisq.test(d.c$gender, d.c$cond)
chisq.test(d.c$disadvantaged, d.c$cond)
chisq.test(d.c$firstgen, d.c$cond)

chisq.test(d.c$race_amaj, d.c$cond)
chisq.test(d.c$race.w, d.c$cond)
chisq.test(d.c$race.a, d.c$cond)
chisq.test(d.c$race.b, d.c$cond)
chisq.test(d.c$race.h, d.c$cond)
chisq.test(d.c$race.n.pi, d.c$cond)

chisq.test(d.c$tobaccouse_yes, d.c$cond)
chisq.test(d.c$bingedrink_yes, d.c$cond)

options(contrasts = c("contr.helmert", "contr.poly"))

Anova(lm(bmi ~ cond, data = d.c))
lm(bmi ~ cond, data = d.c) %>% summary
Anova(lm(age_4y ~ cond, data = d.c))
lm(age_4y ~ cond, data = d.c) %>% summary
Anova(lm(sattoact ~ cond, data = d.c))
lm(sattoact ~ cond, data = d.c) %>% summary
```
